Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-23 DGMM2025/paper.tex
added text for section 4

    % Explain how i use the resulting visibility to compute the normals

    % Then same with curvatures

    % Graphical result comparison of curvatures

>>>>

    Let $V$ the visibility around the point $p$, let $c$ be the centroid of the
    visible points around p. The normal $\vec{n}$ is defined as the first
    eigenvector of the covariance matrix \Nu of the visible points:
    \begin{equation}
        \Nu = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
    \end{equation}
    In order to reorient the normal, we use the trivial normal of the
    surface as a reference.

    Then, to compute the curvatures, we use the Corrected Normal Current
    estimator~\cite{lachaud:2022-dcg} which are based on the normals computed
    above.
